---
title: "Self Assessment: Session 2"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```
# Self Assessment: Session 2

## Instructions

**Welcome!**

*This app is still very nascent, please alert me to any errors or unexpected behaviour.*

Use the chinook.db to answer these questions.
 
**Click Next Topic when you're ready to begin**

## SELECT

```{r select, echo=FALSE}
quiz(
    question("Which of the following SELECT statements are syntactically correct (even if not meaningful)?",
    answer("`SELECT 1 * 5`", correct = TRUE),
    answer("`SELECT 2025 as thisyear`", correct = TRUE),
    answer("`SELECT thomas as instructor`"),
    answer("`SELECT '2025-06-20' as summer solstice`")
    ,allow_retry = TRUE
    ,random_answer_order = TRUE
  ),
  question("Which of the following SELECT statements are valid?",
    answer("`SELECT * FROM Artist`", correct = TRUE),
    answer("`SELECT ArtistId,Name FROM Artist`", correct = TRUE),
    answer("`SELECT ALL FROM Artist`" ),
    answer("`SELECT Artist`"),
    answer("`SELECT AlbumID,ArtistID,Name FROM Artist`")
    ,allow_retry = TRUE
    ,random_answer_order = TRUE
  ),
  question("Which of the following SELECT statements will sort the Invoice table by the smallest Total values?",
  answer("`SELECT * FROM Invoice ORDER BY Total`", correct = TRUE),
  answer("`SELECT InvoiceId, CustomerId, InvoiceDate FROM Invoice ORDER BY Total`", correct = TRUE),
  answer("`SELECT * FROM Invoice ORDER BY Total ASC`", correct = TRUE),
  answer("`SELECT * FROM Invoice SORT BY Total ASC`")
  ,allow_retry = TRUE
  ,random_answer_order = TRUE
  )
)
```

## WHERE

```{r where, echo=FALSE}
quiz(
  question("Which of the following WHERE clauses correctly filters results to show customers who reside in either 'Brazil' or 'Canada'? ",
  answer("`...WHERE Country = 'Brazil' OR 'Canada'`"),
  answer("`...WHERE Country IN ('Brazil' AND 'Canada')`"),
  answer("`...WHERE Country = 'Brazil' AND Country = 'Canada'`"),
  answer("`...WHERE Country = 'Brazil' OR Country = 'Canada'`", correct = TRUE)
  ,allow_retry = TRUE
  ,random_answer_order = TRUE
  ),
  question("Which of the following WHERE clauses correctly filters results to show only employees with the last name 'Mitch'?",
  answer("`...WHERE LastName = 'Mitch'`", correct = TRUE),
  answer("`...WHERE LastName LIKE 'Mitch%'`"),
  answer("`...WHERE LastName LIKE '%Mitch'`", correct = TRUE),
  answer("`...WHERE LastName EXISTS 'Mitch'`")
  ,allow_retry = TRUE
  ,random_answer_order = TRUE
  ),
  question("Which of the following WHERE clauses correctly filters results to show employees with a salary between $92,000 and $117,500?",
  answer("`...WHERE Salary BETWEEN 92000 AND 117500`", correct = TRUE),
  answer("`...WHERE Salary > 92000 AND Salary < 117500`"),
  answer("`...WHERE Salary >= 92000 AND Salary <= 117500`", correct = TRUE),
  answer("`...WHERE Salary IN (92000, 117500)`")
  ,allow_retry = TRUE
  ,random_answer_order = TRUE
  )
)
```


## CASE

```{r case, echo=FALSE}
quiz(
  question("Which of the following CASE statements are syntactically correct?",
  answer("`...CASE WHEN condition THEN result END`", correct = TRUE),
  answer("`...CASE result WHEN condition THEN END`"),
  answer("`...CASE WHEN condition THEN result ELSE alternative_condition END`", correct = TRUE),
  answer("`...CASE WHEN condition THEN result`"),
  answer("`...CASE condition WHEN result THEN END`")
  ,allow_retry = TRUE
  ,random_answer_order = TRUE
  ),

    question("Suppose you want to classify 'rock','alternative', and 'metal' genres into a single category: 'favourites', but want to classify 'Rock And Roll' and 'Blues' into a separate category: 'oldies'. Which of the following CASE statements are correct?",
  answer("```
SELECT DISTINCT Name,
CASE WHEN Name IN ('Rock And Roll','Blues') THEN 'oldies' 
  WHEN Name LIKE '%rock%' OR Name LIKE '%metal%' or Name LIKE '%alt%' 
	THEN 'favourites' 
  ELSE '' END as classify
FROM Genre
```", correct = TRUE),
  answer("```
SELECT DISTINCT Name,
CASE WHEN Name = 'Rock' OR Name LIKE '%metal%' or Name LIKE '%alt%' 
  THEN 'favourites'
  WHEN Name IN ('Rock And Roll','Blues') THEN 'oldies' 
  ELSE '' END as classify
FROM Genre
```", correct = TRUE),
  answer("```
SELECT DISTINCT Name,
CASE WHEN Name LIKE '%rock%' OR Name LIKE '%metal%' or Name LIKE '%alt%' 
	THEN 'favourites' 
  WHEN Name IN ('Rock And Roll','Blues') THEN 'oldies' 
  ELSE '' END as classify
FROM Genre
```"),
  answer("```
SELECT DISTINCT Name,
CASE WHEN Name != 'Rock And Roll' OR Name LIKE '%metal%' or Name LIKE '%alt%' 
	THEN 'favourites' 
  WHEN Name IN ('Rock And Roll','Blues') THEN 'oldies' 
  ELSE '' END as classify
FROM Genre
```")
  ,allow_retry = TRUE
  ,correct = "Correct! While you could write the CASE statement without a LIKE statement and achieve a similar result, there may be more complex scenarios where this is harder. In those instances, the order of the CASE statement is crucial, as once a row is evaluated to meet a criteria, it won't be re-evaluated."
  )
)
```

## JOIN


```{r join, echo=FALSE}
quiz(
  question("Which JOIN types produce NULL values?",
  answer("JOIN"),
  answer("INNER JOIN"),
  answer("LEFT JOIN", correct = TRUE),
  answer("RIGHT JOIN", correct = TRUE),
  answer("FULL OUTER JOIN", correct = TRUE)
  ,allow_retry = TRUE
  ,random_answer_order = TRUE
  ),
  
  question("Which of the following queries correctly joins tables to output all tracks and their corresponding artists and albums?",
    answer("```
SELECT Title, Name, Name 
FROM Album a
INNER JOIN Artist aa
	ON a.ArtistId = aa.ArtistId
INNER JOIN Track t
	ON a.AlbumId = t.AlbumId
```"),
  answer("```
SELECT a.Title, aa.Name, t.Name 
FROM Album a
INNER JOIN Artist aa
	ON a.ArtistId = aa.ArtistId
INNER JOIN Track t
	ON a.AlbumId = t.AlbumId
```", correct = TRUE),
answer("```
SELECT Album.Title as AlbumName, Artist.Name as AristName, Track.Name as TrackName
FROM Album 
INNER JOIN Artist
	ON Album.ArtistId = Artist.ArtistId
INNER JOIN Track
	ON Album.AlbumId = Track.AlbumId
```", correct = TRUE),
answer("```
SELECT Title, Name 
FROM Album a
INNER JOIN Track t
	ON a.AlbumId = t.AlbumId
```")
,allow_retry = TRUE
  ,random_answer_order = TRUE
    ),
  
  question_numeric("Input the correct numeric value (3 digits) putting the JOIN statements in correct order starting `FROM Customer c` in order to see all the tracks purchased by a customer.
                   
      1) ...JOIN Invoice i
      2) ...JOIN Tracks t
      3) ...JOIN InvoiceLine il
              ",
  answer("132", correct = TRUE)
  ,allow_retry = TRUE
  ),
  
  question("If new records were added to the Album table, would the result set change if the join type for the below query was switched to a LEFT JOIN instead?
          
          SELECT a.*, aa.Name
          FROM Album a
          INNER JOIN Artist aa
          	ON a.ArtistId = aa.ArtistId 
          ",
  answer("Results would remain the same", correct = TRUE),
  answer("Results could change")
  ,allow_retry = TRUE
  ,correct = "Correct! Because the Album.ArtistId is the Foreign Key on Artist, we know that there cannot be records in the Album table without a corresponding ArtistId."
  ),
  
    question("If new records were added to the Album table, would the result set change if the join type for the below query was switched to a RIGHT JOIN instead?
          
          SELECT a.*, aa.Name
          FROM Album a
          INNER JOIN Artist aa
          	ON a.ArtistId = aa.ArtistId 
          ",
  answer("Results would remain the same"),
  answer("Results could change", correct = TRUE)
  ,allow_retry = TRUE
  ,correct = "Correct! Though Album.ArtistId is the Foreign Key on Artist, we can have artists in the Artist table without corresponding Albums. In the case of a RIGHT JOIN, we would see NULL values for all a.* columns without a corresponding ArtistId." 
  )
)
```
